Publicity Outreach for ``Quantum interval-valued probability: Contextuality and the Born rule''

### 2018-04-15 revised_prop_letter_publicity.tex
revised_prop_letter_publicity.lyx Updating...

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling
\cite{PironioAcinMassarEtAl2010,MillerShi2016}...\ etc. However,
it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the quantum theory might even be deterministic if it can be simulated
by a deterministic hidden variable model~\cite{EPR1935}. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum} and
Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
theorems respectively exclude any non-local and non-contextuality
deterministic hidden variable model, Meyer claimed that finite-precision
measurements invalidate the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751},
i.e., quantum theory with finite-precision measurements might be non-contextual.
In our investigation~\cite{THOS2017}, we employ an interval-valued
framework to establish bounds on the validity of the Kochen-Specker
theorem in realistic experimental environments. In another word, when
physical measurements are precise enough, the Kochen-Specker theorem
remains valid, i.e., quantum theory remains contextual. Hence, our
results provide additional trust of the randomness of quantum theory.

>>>>

\maketitle
Randomness is used in cryptography, randomized algorithms, and gambling
\cite{PironioAcinMassarEtAl2010,MillerShi2016}...\ etc. However,
it is impossible to prove randomness definitely \cite{Kleppe2004,Shi2015,Random2018}.
While some people believed quantumness implies randomness \cite{Colbeck2006,Shi2015,MillerShi2016,Yuan2017},
the quantum theory might even be deterministic if it can be simulated
by a deterministic hidden variable model~\cite{EPR1935}. Although
the Bell \cite{Bell1964,Redhead1987-REDINA,peres1995quantum} and
Kochen-Specker \cite{BELL_1966,kochenspecker1967,Redhead1987-REDINA,peres1995quantum}
theorems respectively exclude any local and non-contextuality hidden
variable model, Meyer claimed that finite-precision measurements invalidate
the spirit of the Kochen-Specker theorem~\cite{PhysRevLett.83.3751},
i.e., quantum theory with finite-precision measurements might be non-contextual.
In our investigation~\cite{THOS2017}, we employ an interval-valued
framework to establish bounds on the validity of the Kochen-Specker
theorem in realistic experimental environments. In another word, when
physical measurements are precise enough, the Kochen-Specker theorem
remains valid, quantum theory remains contextual, and our results
provide additional trust of the randomness of quantum theory.
